Group meetings

### 2023-06-26 diapo/26-06-23_meeting/main.tex
New group meeting

\date{05/06/2023}

@@

\begin{frame}<1>[label=prob]
  \frametitle{Problems/doubts}
  \begin{itemize}
    \item<1-> The memory doesn't output the right values
    \item<2-> The memory input seems to be active for too long
    \item<3-> The output of the sigmoid doesn't look right
    \item<4-> The output result isn't what is expected
  \end{itemize}
\end{frame}

@@

\againframe<4>{prob}
\begin{frame}{Problems/doubts}
  The output is ~0.791 V. This is $-1.09$ and should be $0.015$

  \centering
  \includegraphics[width=\textwidth]{fulltrial1/fulltrial1-final-res}
\end{frame}

@@

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{4cm} }
    \rowcolor{firstRow}
    \color{white}\textbf{\#} & \centering\color{white}Task \cr
    1 & Find another LSTM problem \\
    2 & "Debug" the circuit \\
    2.1 & Run the entire simulation \\
    3 & Work on thesis \\
  \end{tabular}
\end{frame}

>>>>

\date{12/06/2023}

@@

\begin{frame}<1>[label=prob]
  \frametitle{Problems/doubts}
  \begin{itemize}
    \item<1-> The memory doesn't output the right values
    \item<2-> The memory input seems to be active for too long
    \item<3-> The output of the sigmoid doesn't look right (Now fixed)
    \item<4-> The output result isn't what is expected (Scale issue)
  \end{itemize}
\end{frame}

@@

\begin{frame}{Problems/doubts}
  To fix that I had to re-adjust the reference voltages (sigmoid):
  \begin{figure}[!tbp]
    \centering
    \begin{minipage}[b]{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{activation/sigmoid}
      \caption{before}
    \end{minipage}
    \hspace{20pt}
    \begin{minipage}[b]{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{activation/realSigmoid}
      \caption{after}
    \end{minipage}
  \end{figure}
\end{frame}

\begin{frame}{Problems/doubts}
  To fix that I had to re-adjust the reference voltages (tanh):
  \begin{figure}[!tbp]
    \centering
    \begin{minipage}[b]{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{activation/tanh}
      \caption{before}
    \end{minipage}
    \hspace{20pt}
    \begin{minipage}[b]{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{activation/realTanh}
      \caption{after}
    \end{minipage}
  \end{figure}
\end{frame}

\againframe<4>{prob}
\begin{frame}{Problems/doubts}
  The output is weirdly on a different scale but gives out the right overall values. (Scale factor ~9022)

  \centering
  \includegraphics[width=.8\textwidth]{output/results0}
\end{frame}

@@

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{6cm} }
    \rowcolor{firstRow}
    \color{white}\textbf{\#} & \centering\color{white}Task \cr
    1 & Find another LSTM problem \\
    2 & Find out what is causing the issue \\
    3 & Find formula for approximate onChip area \\
    4 & Work on thesis \\
  \end{tabular}
\end{frame}
